Brownian Dynein Model

### 2015-07-30 latex/derivation.tex
add a simplified expression for X_3 as an example

\begin{multline}
  X_3 = \mn \frac{\sin(\Theta_{ml})F_{xt } + \mn \cos(\Theta_{ml})F_{yt } + \sin(\Theta_{ml})F_{xmr} + \mn \cos(\Theta_{ml})F_{ymr} + \sin(\Theta_{ml})F_{xbr} + \mn \cos(\Theta_{ml})F_{ybr}}{\gamma L_s} + \\
	\mn \frac{\sin(\Theta_{ml})R_{xt } + \mn \cos(\Theta_{ml})R_{yt } + \sin(\Theta_{ml})R_{xmr} + \mn \cos(\Theta_{ml})R_{ymr} + \sin(\Theta_{ml})R_{xbr} + \mn \cos(\Theta_{ml})R_{ybr}}{L_s}
\end{multline}

>>>>

\begin{multline}
  X_3 = \mn \frac{\sin(\Theta_{ml})F_{xt } + \mn \cos(\Theta_{ml})F_{yt } + \sin(\Theta_{ml})F_{xmr} + \mn \cos(\Theta_{ml})F_{ymr} + \sin(\Theta_{ml})F_{xbr} + \mn \cos(\Theta_{ml})F_{ybr}}{\gamma L_s} + \\
	\mn \frac{\sin(\Theta_{ml})R_{xt } + \mn \cos(\Theta_{ml})R_{yt } + \sin(\Theta_{ml})R_{xmr} + \mn \cos(\Theta_{ml})R_{ymr} + \sin(\Theta_{ml})R_{xbr} + \mn \cos(\Theta_{ml})R_{ybr}}{L_s}
\end{multline}
The following is David's simplification of $X_3$:
\begin{align}
  X_3 &= -\frac{1}{L_s}\left\{ \sin(\Theta_{ml})\left(\frac{F_{xt}+F_{xmr}+F_{xbr}}{\gamma} + R_{xt }+R_{xmr}+R_{xbr}\right) -
    \cos(\Theta_{ml})\left(\frac{F_{yt }+F_{ymr}+F_{ybr}}{\gamma} +
    R_{yt}+R_{ymr}+R_{ybr}\right) \right\}
    \\
    &?= \frac{\hat{a}_{ml}\cdot \vec{F}_{tot_{ml}}}{\gamma L_s}
\end{align}
where $\hat a$ is a unit vector in a the direction related to the $ml$
segment, and $\vec{F}_{tot_{ml}}$ is a total force of some sort,
including the random fluctuations.  I don't think we want to write the
formula in this final way, but it may help in thinking about the
equations.  I certainly think that the form with just one $\sin$ and
one $\cos$ is an improvement, and reduces the likelihood of
introducing sign errors (or sine errors, for that matter).
